---
title: "Speech Analysis"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = T, echo = FALSE, warning = F, message = F)
```

```{r library and data}
library(syuzhet)
library(ggplot2)
library(dplyr)
library(wordcloud)
library(SnowballC)
library(gridExtra)
library(stringr)
library(readr)
library(tidytext)
library(tidyverse)
library(tm)
library(qdap)
library(plotly)
content<- read_file("I_Have_A_Dream.txt")
content2 <- read_file("The awakening.txt")
```

## Frequency of words
```{r freq}
cleancont <- rm_stopwords(content2, Top200Words)
frequency <- all_words(cleancont, "")
freqss<- frequency
freq_s<- freqss%>%
  group_by(FREQ)

freq_ss <- arrange(freq_s, desc(FREQ))%>%
  head(7)

bar<- ggplot(freq_ss)+
  geom_bar(aes(x = WORD, y = FREQ, fill = WORD), stat = "identity")+
  theme(aspect.ratio = 1) +
  labs(x = NULL, y = NULL)
bark<- bar + coord_polar()
bark

```

## Sentence length

```{r sentence length}
dfsent <- tibble(
  Sent = get_sentences(content),
  Number = seq_along(Sent)
)
df_sentencelength<- dfsent%>%
  mutate(`Sentence length` = wc(dfsent$Sent))
head(df_sentencelength)

ggplot_sentence_length<- ggplot(df_sentencelength)+
  geom_line(aes(x = Number, y = `Sentence length`))
ggplot_sentence_length

library(plotly)
ggplotly(ggplot_sentence_length)
```

The mean value & SD of the sentence length is:
```{r sent length}
tibble(
mean = mean(df_sentencelength$`Sentence length`),
StandardDiviation = sd(df_sentencelength$`Sentence length`)
)
```


## Syllable count per word

```{r}
word<- str_split(content, boundary("word"))[[1]]
several<- sort(table(word), decreasing=T)
syl <- as.data.frame(several) %>%
  mutate(syllable = syllable_sum(word))
head(syl)
```


## Frequency of use of adj, adv, gerunds, participles, infinitives, prepositions
```{r}

```

## punctuation type and frequency

```{r}
tibble(
  Comma = str_count(content, ","),
  Semicolons = str_count(content, ";"),
  Colons = str_count(content, ":"),
  Dashes = str_count(content, "-"),
  QuestionMarks = sum(gregexpr("[?]", content)[[1]] > 0),
  Exclamation = sum(gregexpr("[!]", content)[[1]] > 0),
  Parenthese = sum(gregexpr("[(]", content)[[1]] > 0)
)
```


## Overuse of comma

```{r}
CommaSentence <- dfsent%>%
  select(Sent)
CommaSent <- tibble(
  Sent = get_sentences(content),
  Number = seq_along(Sent),
  Comma = str_count(CommaSentence[[1]], ",")
)
Com<- ggplot(CommaSent)+
  geom_point(aes(x = Number, y = Comma))
Com

df_sentencelength


```
t-test
boxp for each file (length of sent, word, overuse of comma)
should be able to compare.


```{r}
ggplot(CommaSent) +
  geom_bar(aes(x = Comma, stat = "identity"))
```

```{r}
dfsent2 <- tibble(
  Sent = get_sentences(content2),
  Number = seq_along(Sent)
)
CommaSentence2 <- dfsent2%>%
  select(Sent)
CommaSent2 <- tibble(
  Sent = get_sentences(content2),
  Number = seq_along(Sent),
  Comma = str_count(CommaSentence2[[1]], ",")
)

CommaSent$Passage <- 1
CommaSent2$Passage <- 2

df <- rbind(CommaSent, CommaSent2)

ggplot(df) +
  geom_boxplot(aes(x = factor(Passage), y = Comma, fill = factor(Passage)))
ggplotly()

wilcox.test(CommaSent$Comma, CommaSent2$Comma)
```

The p-value is greater than 0.05, then we fail to reject hypothesis H0 of statistical difference in the means of two groups.
