---
title: "Text analysis and comparison application"
runtime: shiny
output: html_document
author: Frank Zhang
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Project brief
This project aims on generating a text analysis report with the selected file. Since we don't want a report that only works for a single file, a shiny interactive application is created, allowing the user to select whatever text file they want to analyze. On the other hand, some may want to compare and contrast two texts at the same time. To achieve this, the shiny application is consisted of two sides; in each side, the user can select a file individually; two reports will be finally generated by the application. 
To see the individual shiny app, please visit [Shiny App](https://ziyuezhang.shinyapps.io/compare_texts/).

### Introduction to the shiny app
The application contains five different functions: Top seven words appeared in the text, A statistics of sentence length, count of frequency and syllble of all the words in the text, Puncuation type and frequency, and the use of comma.

-Top seven words: This function will show you the top seven words in the text, as the name refers. These words can somehow help you with a better understanding of the text. 

-Sentence length statistic: This function will show you both the exact length of each sentence and the average length of the sentences. For the reason that there might be too many sentences exist in a text, and it will be quite hard to find out the length of each sentence, a smooth curve is added to show you the general trend.

-Syllable count: The following table will show you the entire wordbase of the text, which means that it contains every single word appeared in the text. You can search any word for its frequency in the text, and its syllable count. Also, you can either choose to see which word has the most/least frequency and syllable. 

-Puncuation: This is just a report of puncuation types and frequency in the text.

-Use of comma: This part contains two plots. In the first plot, it will give you the number of comma and their frequency in the text. For example: In a sentence, a comma count of 4 appears in the text for 100 times. On the other hand, the right plot is a display of all the comma count for every sentence, but it will not work well with large text because of the overlap.

To use the shiny app, click "Browse" to input file. There are explanations for each of the function, click "Click me for explanation" for the explanations.

### Shiny Application
```{r tabsets, echo=FALSE}
shinyAppDir(("/Users/zhangziyue/Documents/2016_DS_Class_Clint_Frank_Text.git"),
  options = list(
    width = 1000, height = 950
  )
)
```

